An Accurate Model for SARS-CoV-2 pooled RT-PCR Test Errors

### 2021-03-21 comment.tex
uri commentz

\section{Introduction}
Reverse transcription polymerase chain reaction (RT-PCR) testing is a
key component in breaking transmission chains and mitigating the
COVID-19 pandemic. As such, the need for large-scale testing has
resulted in the development of techniques to increase the the
throughput of RT-PCR tests \cite{DorfmanYuvalDor, PoolSize30,
  BayesianDorfman, MatrixPooling, LionDorfman}. These techniques, often termed
 \emph{pooling}, or group testing,  have originated in the seminal work of Dorfman et al. and their pooling technique
 \cite{DorfmanOriginal, DorfmanYuvalDor}. Under Dorfman pooling, one selects $N$
individuals and performs a single RT-PCR test on their combined
(\emph{pooled}) samples. If the pooled test yields a positive result, then  each individual is retested separately; otherwise, everyone is declared negative. The throughput efficiency of
Dorfman pooling for has been demonstrated empirically
\cite{DorfmanYuvalDor} and its error rates thoroguhly investigated
\cite{Kim, Simplistic1, OptimalDorfmanPool}.

Pooling RT-PCR tests is not perfect, and there is always some nonzero
probability of error. Typically, previous research assumed that the probability of a true-positive (the test's \emph{sensitivity}) does not depend on the
number of infected samples in the pool, but rather on the existence of
at least one such sample. Thus, the probability of a positive result
in a pooled test has been (assumed) identical for a pool with one sample
from an infected individual and, e.g., five such samples. This
assumption is common in the group testing literature \cite{Kim,
  OptimalDorfmanPool}, as well as in more specific, COVID-19 focused
studies \cite{Simplistic1, Simplistic2}. In this study we refute these
commonly made assumptions and show how using a more accurate probabilistic model affects estimation of
false-negative rates for Dorfman pooling.

>>>>

\section{Introduction}
Reverse transcription polymerase chain reaction (RT-PCR) testing is a
key component in breaking transmission chains and mitigating the
COVID-19 pandemic. As such, the need for large-scale testing has
resulted in the development of techniques to increase the the
throughput of RT-PCR tests \cite{DorfmanYuvalDor, PoolSize30,
  BayesianDorfman, MatrixPooling, LionDorfman}. These techniques, often termed
 \emph{pooling}, or group testing, have originated in the seminal work of Dorfman and his pooling technique
 \cite{DorfmanOriginal, DorfmanYuvalDor}. Under Dorfman pooling, one selects $N$
individuals and performs a single RT-PCR test on their combined
(\emph{pooled}) samples. If the pooled test yields a positive result, then each individual is retested separately; otherwise, everyone is declared negative. The throughput efficiency of
Dorfman pooling for has been demonstrated empirically
\cite{DorfmanYuvalDor} and its error rates thoroguhly investigated
\cite{Kim, Simplistic1, OptimalDorfmanPool}.

Previous studies assumed that the probability of a true-positive (the test's \emph{sensitivity}) does not depend on the
number of infected samples in the pool, but rather on the existence of
at least one such sample. Thus, the probability of a positive result
in a pooled test has been (assumed) identical for a pool with one sample
from an infected individual and, e.g., five such samples. This
assumption is common in the group testing literature \cite{Kim,
  OptimalDorfmanPool}, as well as in more specific, COVID-19 focused
studies \cite{Simplistic1, Simplistic2}. In this study we challenge these
commonly made assumptions and show how using a more accurate probabilistic model affects estimation of
false-negative rates for Dorfman pooling.
